Evolutionary Quantum Transition (EQUATe): A Novel Solution to Optimization Problems \\

### 2020-10-05 paper_nit.tex
Final_v

\section{Computing Methologies}

@@

\subsection{A Novel Ensemble}
As we have seen, each vertical offers it's own advantages and disadvantages when it comes to solving an optimization problem. A trade-off exists between CC and QC when it comes to delivering quality results in a reduced time frame and availability of resources to implement the search process. Meanwhile, EC offers a multi-pronged approach to the search process by applying certain constraints and operators which results in the emergence of the best results with a decreased time complexity. EQUATe borrows the most promising concepts from QC and EC to provide a new front to solving optimization problems. The space-saving capabilities offered by QC are excellent additions to EQUATe. Likewise, the evolutionary model offered by EC boosts the search process. The general MOOP is a relatively broad set of problems, with each problem requiring certain tweaks to the solution search process. In this paper, we narrow down the MOOPs to a specific case i.e, Design a circuit to achieve state $j$ from $i$ with multiple cost considerations. 
% \subsection{Computing Methodologies}
% 
% Most form of computational algorithms in the present day, are executed on a conventional computer. The fundamental notation used for differentiating Classical Computing (CC) and QC \cite{nara} is the basic unit of information. While classical computers use bits 0 and 1, quantum computers use "one of" two computational basis states. The label awarded to these states is "bra-ket" notation i.e, state $\ket{0}$ or $\ket{1}$. Bits are assigned states 0 or 1 deterministically and independently. However, qbuits can exist in a superposition state of $\alpha\textsubscript{0}$$\ket{0}$ + $\alpha\textsubscript{1}$$\ket{1}$, where $\alpha{0}$ and $\alpha{1}$ are complex numbers, such that $|\alpha\textsubscript{0}|\textsuperscript{2}$ + $|\alpha\textsubscript{1}|\textsuperscript{2}$ = 1.
%

@@

\section{Evolved Quantum Computing}

Evolved self-organizing computer programs \cite{self} utilize the techniques described in the previous section to solve problems. In this paper the following general problem structure is considered for demonstrating the capabilities of EQUATe; How to design a circuit to travel from state $\textit{A}$ to state $\textit{B}$? These problem types are called "Oracle Analysis" as they require we to determine some property of a valid quantum gate with no prior information on the intermediate states and what combination of gates results in what output. Some of the key terminologies used in the following texts are explained in Table $\ref{tab:2}$

@@

\subsection{EQUATe Approach}

@@

>>>>

\section{Computing Methology}

@@

\subsection{EQUATe: A Novel Ensemble}
As we have seen, each vertical offers it's own advantages and disadvantages when it comes to solving an optimization problem. A trade-off exists between CC and QC when it comes to delivering quality results in a reduced time frame and availability of resources to implement the search process. Meanwhile, EC offers a multi-pronged approach to the search process by applying certain constraints and operators which results in the emergence of the best results with a decreased time complexity. EQUATe borrows the most promising concepts from QC and EC to provide a new front to solving optimization problems. The space-saving capabilities offered by QC are excellent additions to EQUATe. Likewise, the evolutionary model offered by EC boosts the search process. The general MOOP is a relatively broad set of problems, with each problem requiring certain tweaks to the solution search process. In this paper, we narrow down the MOOPs to a specific case i.e, Design a circuit to achieve state $j$ from $i$ with multiple cost considerations. 
% \subsection{Computing Methodologies}
% 
% Most form of computational algorithms in the present day, are executed on a conventional computer. The fundamental notation used for differentiating Classical Computing (CC) and QC \cite{nara} is the basic unit of information. While classical computers use bits 0 and 1, quantum computers use "one of" two computational basis states. The label awarded to these states is "bra-ket" notation i.e, state $\ket{0}$ or $\ket{1}$. Bits are assigned states 0 or 1 deterministically and independently. However, qbuits can exist in a superposition state of $\alpha\textsubscript{0}$$\ket{0}$ + $\alpha\textsubscript{1}$$\ket{1}$, where $\alpha{0}$ and $\alpha{1}$ are complex numbers, such that $|\alpha\textsubscript{0}|\textsuperscript{2}$ + $|\alpha\textsubscript{1}|\textsuperscript{2}$ = 1.
%

@@

\section{Evolutionary Quantum Transition (EQUATe)}

Evolved self-organizing computer programs \cite{self} utilize the techniques described in the previous section to solve problems. In this paper the following general problem structure is considered for demonstrating the capabilities of EQUATe; How to design a circuit to travel from state $\textit{A}$ to state $\textit{B}$? These problem types are called "Oracle Analysis" \cite{oracle} as they require we to determine some property of a valid quantum gate with no prior information on the intermediate states and what combination of gates results in what output. Some of the key terminologies used in the following texts are explained in Table $\ref{tab:2}$

@@

\subsection{The EQUATe Approach}

@@

\bibitem{oracle} J. Chen et al., "Supporting oracle construction via static analysis," 2016 31st IEEE/ACM International Conference on Automated Software Engineering (ASE), Singapore, 2016, pp. 178-189.
